### 2014-03-02 paper/related.tex

Designed to target legacy code, secure multi-execution (SME) is a black-box
technique to enforce information-flow control~\cite{Devriese:2010}. It runs
multiple copies of the program, one per security level, where the semantics of
I/O interactions is altered. Besides its black-box nature, authors often present
it considering one specific programming
language~\cite{KULeuven-350547,Rafnson:2013}. Differently, Bielova
al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
details of the underlying language is hidden.  Zanarini et
al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
interaction trees~\cite{jacobs-tutorial}, which threats programs as black-boxes
about which nothing is known except what is inferred from their I/O interactions
with the environment. Similar to SME, our approach only mediates some I/O
operations; differently, it runs the program once.

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in less false alarms and target legacy code, it comes at the
cost of complexity (the system must accomodate the entirety of JavaScript's
semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
higher than 100\%!\cite{JSFlow}.  Alternatively, coarse-grained approaches have
also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}. Different
from them, we rely on programming level abstraction to isolate
computations.

>>>>

One information flow control technique designed to handle legacy code is
secure multi-execution (SME)~\cite{Devriese:2010}. It runs
multiple copies of the program, one per security level, where the semantics of
I/O interactions is altered. Authors often present
SME considering one specific programming
language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova
al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
details of the underlying language is hidden.  Zanarini et
al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
interaction trees~\cite{jacobs-tutorial}, which treats programs as black-boxes
about which nothing is known except what is inferred from their I/O interactions
with the environment. Similar to SME, our approach mediates I/O
operations; however, our approach only runs the program once.

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in less false alarms and target legacy code, it comes at the
cost of complexity (the system must accomodate the entirety of JavaScript's
semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
higher than 100\%!~\cite{JSFlow}.  Alternatively, coarse-grained approaches have
also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}. \Red{Different
from them, we rely on programming level abstraction to isolate
computations.}
